Look, we can do something

### 2024-10-22 paper.tex
Rework definition of awesomeness (1/N)

\section{A new pore shape parameter}
We propose a new parameter for shape description which is based on the idea of
numerical assession of bottlenecks in pores. For simplicity, we will assume
that our pore is 1-connected. Suppose you have a round pore in the form close to
a disk and another pore in the form of a dumbbell. We want to develop a
parameter which would be close to 1 for the first pore and close to 0 for the
second. For this purpose we want to visit all points which lie on the pore's
boundary and find a pair of points which form a bottleneck, i.e have a small
distance between each other. Obviously, not all pairs of points which are close
to each other form a bottleneck. Namely, on \cref{fig:parameter} points $A$ and
$B$ form a bottleneck and points $A$ and $C$ do not form it. If you choose a
point $O$ which lies outside of the pore and travel along the pore's boundary in
one direction (either clockwise or counter-clockwise), when you arrive at $A$
you will see the point $O$ to your left and when you are in $B$ you will see $O$
to your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to
the same side from you. Instead of doing this check for ``bottleneckness'', we
add a penalty coefficient to the distance between points, namely for a pair of
points $(A, B)$ we calculate the following:
\begin{equation}
  p_{AB} = \rho_{AB} / L_{AB}
  \label{eq:intro}
\end{equation}
where $\rho_{AB}$ is the Euclidean distance between $A$ and $B$ and $L_{AB}$ is
the length of a pore's boundary segment with end points $A$ and $B$ (there are
two such segments, you need to take the segment with minimal length). Suppose
$B$ is a set of all points on the pore's boundary. We define a new pore shape
parameter $p$, called ``\highlight{awesomeness}'', using \ref{eq:intro}:
\begin{equation}
  p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
  \label{eq:awesomeness}
\end{equation}
Obviously, it's unlikely that $p$ = $p_{AC}$ because $L_{AC} \approx \rho_{AC}$.
It's easy to see that $0 \le p \le 1$ because $0 \le \rho_{AB} \le L_{AB}$ for
any $A$ and $B$ for a line segment which connects $A$ and $B$ is the shortest
of all other curves which connect those points.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/parameter.png}
  \caption[]{A dumbbell-like boundary of a pore. Points $A$ and $B$ form a
    bottleneck while points $A$ and $C$ do not. This can seen by a relative
    position of the point $O$ while traversing the boundary
    counter-clockwise. Namely, it's on the left side when crossing $A$ but on
    the right side when crossing $B$. When crossing $A$ and $C$, the relative
    position of $O$ does not change. The parameter $p_{AB}$ is equal to the
    distance between $A$ and $B$ divided by length of the blue contour $L$.}
  \label{fig:parameter}
\end{figure}

@@

Although a guaranteed upper bound for awesomeness is 1, it's reachable only for
degenerate shapes in the form of line segments. The biggest value for
non-degenerate shapes is reached for a disk and equals to $2/\pi$.

@@

It can be seen that if a pore has low convexity ($< 0.6$)
\highlight{awesomeness} adds no information to the pore's descriptors because it
stays relatively low for all pores. When, however, the convexity is high it adds
a new dimension to the parameter space. \highlight{Awesomeness} also correlates
with elongation, but this correlation can be reduced. Remember, that a disk has
the biggest known \highlight{awesomeness}. Similarly, an ellipse defined as
\begin{equation*}
  \frac{x^2}{a^2} + \frac{y^2}{b^2} = 1
\end{equation*}
has the biggest known \highlight{awesomeness} from all shapes with elongation
$E = a / b$ (suppose $a \le b$) (see \cref{fig:ae-space}). Using Ramanujan's
formular for the perimeter of an ellipse we get
\begin{equation*}
  p \le p_{ellipse} = \frac{2a}{P/2} \approx \frac{4E}{\pi[3(1+E) - \sqrt{(3E+1)(E+3)}]}
\end{equation*}
By dividing \highlight{awesomeness} by $p_{ellipse}$ we obtain an improved
parameter $p'$:
\begin{equation}
  p' = \frac{\pi p [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E}
  \label{eq:improved-awesomeness}
\end{equation}
Indeed, on \cref{fig:caei-space} we see that improved awesomeness is less
correlated with elongation.

>>>>

\section{A new pore shape parameter}
We propose a new parameter for shape description which is based on the idea of
numerical assession of bottlenecks in pores. For simplicity, we will assume
that our pore is 1-connected. Suppose you have a round pore in the form close to
a disk and another pore in the form of a dumbbell. We want to develop a
parameter which would be close to 1 for the first pore and close to 0 for the
second. For this purpose we want to visit all points which lie on the pore's
boundary and find a pair of points which form a bottleneck, i.e have a small
distance between each other. Obviously, not all pairs of points which are close
to each other form a bottleneck. Namely, on \cref{fig:parameter} points $A$ and
$B$ form a bottleneck and points $A$ and $C$ do not form it. If you choose a
point $O$ which lies outside of the pore and travel along the pore's boundary in
one direction (either clockwise or counter-clockwise), when you arrive at $A$
you will see the point $O$ to your left and when you are in $B$ you will see $O$
to your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to
the same side from you. Instead of doing this check for ``bottleneckness'', we
add a penalty coefficient to the distance between points, namely for a pair of
points $(A, B)$ we calculate the following:
\begin{equation}
  p_{AB} = \rho_{AB} / L_{AB}
  \label{eq:intro}
\end{equation}
where $\rho_{AB}$ is the Euclidean distance between $A$ and $B$ and $L_{AB}$ is
the length of a pore's boundary segment with end points $A$ and $B$ (there are
two such segments, you need to take the segment with minimal length). Suppose
$B$ is a set of all points on the pore's boundary. We define a new pore shape
parameter $p$ using \ref{eq:intro}:
\begin{equation}
  p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
  \label{eq:pre-awesomeness}
\end{equation}
Obviously, it's unlikely that $p$ = $p_{AC}$ because $L_{AC} \approx \rho_{AC}$.
It's easy to see that $0 \le p \le 1$ because $0 \le \rho_{AB} \le L_{AB}$ for
any $A$ and $B$ for a line segment which connects $A$ and $B$ is the shortest
of all other curves which connect those points.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/parameter.png}
  \caption[]{A dumbbell-like boundary of a pore. Points $A$ and $B$ form a
    bottleneck while points $A$ and $C$ do not. This can seen by a relative
    position of the point $O$ while traversing the boundary
    counter-clockwise. Namely, it's on the left side when crossing $A$ but on
    the right side when crossing $B$. When crossing $A$ and $C$, the relative
    position of $O$ does not change. The parameter $p_{AB}$ is equal to the
    distance between $A$ and $B$ divided by length of the blue contour $L$.}
  \label{fig:parameter}
\end{figure}

Although a guaranteed upper bound for $p$ is 1, it's reachable only for
degenerate shapes in the form of line segments. The biggest value for
non-degenerate shapes is reached for a disk and equals to $2/\pi$. Similarly, an
ellipse defined as
\begin{equation*}
  \frac{x^2}{a^2} + \frac{y^2}{b^2} = 1
\end{equation*}
has the biggest known value of $p$ from all shapes with elongation $E = a / b$
(suppose $a \le b$). Using Ramanujan's formula for the perimeter of an ellipse
we get
\begin{equation*}
  p \le p_{ellipse} = \frac{2a}{P/2} \approx \frac{4E}{\pi[3(1+E) - \sqrt{(3E+1)(E+3)}]}
\end{equation*}
where $P$ is a perimeter of the ellipse. By dividing $p$ by $p_{ellipse}$ we
obtain an improved pore shape parameter $P$:
\begin{equation*}
  P = \frac{\pi p [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E}
\end{equation*}

Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
shape parameter we call ``\highlight{awesomeness}'':
\begin{equation}
  \begin{aligned}
    P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2\}
  \end{aligned}
  \label{eq:awesomeness}
\end{equation}
where, again, $E$ is the elongation and $B$ is the boundary of the pore.

@@

@@

It can be seen that if a pore has low convexity ($< 0.6$)
\highlight{awesomeness} adds no information to the pore's descriptors because it
stays relatively low for all pores. When, however, the convexity is high it adds
a new dimension to the parameter space.

% CHECK THIS:
Indeed, on \cref{fig:caei-space} we see that improved awesomeness is less
correlated with elongation.
